Revisited hidden weight bit function

### 2024-11-05 RevisedHiddenWeight.tex
Minors

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		$a$ & $(0,0)$ & $(0,1)$ & $(1,1)$ \\ \hline
		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\ \hline
		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\ \hline
		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\ \hline
	\end{tabular}
	\caption{Values of $\Dnka{2}{k}{a}$}\label{tab:Dnka}
\end{table}

@@

Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
\[ \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.\]
\end{proof}

@@

    \begin{table}
    	\centering
    	\begin{tabular}{|c|c|}
    		\hline
    		$k$ & $\Dnka nka$\\ \hline
    		$0$&$1$\\ \hline
            $1$&$2(p-q)$\\ \hline
            $2$&$2(p-q)^2-3(p+q)+r$\\ \hline
            $3$&$\frac 23(p-q)\left(2(p-q)^2-9(p+q)+3r+7\right)$\\ \hline
    	\end{tabular}
    	\caption{Values of $\Dnka{n}{k}{a}$ for small values of $k$}\label{tab:Dnka_small_k}
    \end{table}
\end{remark}

@@

	We prove that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$ by showing that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$.
    %It remains to prove that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$. 
    Using that $|w|^2=w\overline w$ for every complex number $w$, we obtain for all $z\in \dis$:
    \[
        \left|-z^2+2z+1\right|^2=\left(z^2-2z-1\right)\left(\overline z^2-2\overline z-1\right)=6-\left(z^2+\overline z^2\right)=6-2\mathrm{Re}\left(z^2\right),
    \]
    where $\mathrm{Re}\left(z^2\right)$ denotes the real part of $z^2$. Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $\dis$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ is $6-2(-1)=8$.

@@

	\begin{align*}
\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,2t}(y)+b \cdot y} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.%\qedhere
\end{align*}

@@

    \begin{figure}
    	\centering
    	\includegraphics[width=9cm]{family_curves_g.pdf}
    	\caption{The curves of $\alpha\mapsto g_\lambda(\alpha)$ for the values $\lambda=\frac{i}{25}$ from $i=0$ (blue) to $i=24$ (red).}
    	\label{fig:family_curves_g}
    \end{figure}

@@

\iffalse
\begin{table}
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
		$2$  & $2$     & $4$     \\
		$4$  & $8$     & $14$     \\
		$6$  & $20$    & $36$    \\
		$8$  & $52$    & $114$    \\
		$10$ & $108$   & $288$   \\
		$12$ & $292$   & $820$   \\
		$14$ & $700$   & $2\,316$  \\
		$16$ & $2\,176$  & $6\,006$  \\
		$18$ & $4\,964$  & $18\,192$  \\
		$20$ & $14\,968$ & $48\,480$ \\
		$22$ & $34\,232$ & $140\,392$ \\
		$24$ & $109\,648$ & $392\,168$ \\ \hline
	\end{tabular}
	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$}
	\label{table:max_walsh_vs_bound}
\end{table}
\fi

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$  & $\lfloor 1+n \cdot 2^{3n/4} \rfloor$\\ \hline
		$2$  & $2$     & $4$  &  $6$ \\
		$4$  & $8$     & $14$  & $33$  \\
		$6$  & $20$    & $36$   & $136$\\
		$8$  & $52$    & $114$  & $513$ \\
		$10$ & $108$   & $288$  & $1\,811$\\
		$12$ & $292$   & $820$  & $6\,145$ \\
		$14$ & $700$   & $2\,316$ & $20\,275$ \\
		$16$ & $2\,176$  & $6\,006$ & $65\,637$ \\
		$18$ & $4\,964$  & $18\,192$ & $208\,535$ \\
		$20$ & $14\,968$ & $48\,480$ & $655\,361$ \\
		$22$ & $34\,232$ & $140\,392$ & $2\,039 \,002$ \\
		$24$ & $109\,648$ & $392\,168$ & $6\,291 \,457$  \\ \hline
	\end{tabular}
	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$ and the one from Corollary~\ref{cor:bound_walsh_cauchy}.}
	\label{table:max_walsh_vs_bound}
\end{table}

\begin{table}
	\centering
	\begin{minipage}{0.24\textwidth}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			$n$ & $\approx B_n$ \\
			\hline
			$2$  & $4.00 \cdot 10^{0}$  \\
			$4$  & $1.40 \cdot 10^{1}$  \\
			$6$  & $3.60 \cdot 10^{1}$  \\
			$8$  & $1.14 \cdot 10^{2}$  \\
			$10$ & $2.88 \cdot 10^{2}$  \\
			$12$ & $8.20 \cdot 10^{2}$  \\
			$14$ & $2.32 \cdot 10^{3}$  \\
			$16$ & $6.01 \cdot 10^{3}$  \\
			$18$ & $1.82 \cdot 10^{4}$  \\
			$20$ & $4.85 \cdot 10^{4}$  \\
			\hline
		\end{tabular}
	\end{minipage}%
	\begin{minipage}{0.24\textwidth}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			$n$ & $\approx B_n$ \\
			\hline
			$22$ & $1.40 \cdot 10^{5}$  \\
			$24$ & $3.92 \cdot 10^{5}$  \\
			$26$ & $1.14 \cdot 10^{6}$  \\
			$28$ & $3.12 \cdot 10^{6}$  \\
			$30$ & $8.90 \cdot 10^{6}$  \\
			$32$ & $2.50 \cdot 10^{7}$  \\
			$34$ & $7.14 \cdot 10^{7}$  \\
			$36$ & $2.04 \cdot 10^{8}$  \\
			$38$ & $5.75 \cdot 10^{8}$  \\
			$40$ & $1.62 \cdot 10^{9}$  \\
			\hline
		\end{tabular}
	\end{minipage}%
	\begin{minipage}{0.24\textwidth}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			$n$ & $\approx B_n$ \\
			\hline
			$42$ & $4.59 \cdot 10^{9}$  \\
			$44$ & $1.29 \cdot 10^{10}$ \\
			$46$ & $3.63 \cdot 10^{10}$ \\
			$48$ & $1.02 \cdot 10^{11}$ \\
			$50$ & $2.88 \cdot 10^{11}$ \\
			$52$ & $8.06 \cdot 10^{11}$ \\
			$54$ & $2.30 \cdot 10^{12}$ \\
			$56$ & $6.45 \cdot 10^{12}$ \\
			$58$ & $1.83 \cdot 10^{13}$ \\
			$60$ & $5.14 \cdot 10^{13}$ \\
			\hline
		\end{tabular}
	\end{minipage}%
	\begin{minipage}{0.24\textwidth}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			$n$ & $\approx B_n$ \\
			\hline
			$62$ & $1.47 \cdot 10^{14}$ \\
			$64$ & $4.09 \cdot 10^{14}$ \\
			$66$ & $1.17 \cdot 10^{15}$ \\
			$68$ & $3.25 \cdot 10^{15}$ \\
			$70$ & $9.34 \cdot 10^{15}$ \\
			$72$ & $2.60 \cdot 10^{16}$ \\
			$74$ & $7.44 \cdot 10^{16}$ \\
			$76$ & $2.08 \cdot 10^{17}$ \\
			$78$ & $5.97 \cdot 10^{17}$ \\
			$80$ & $1.65 \cdot 10^{18}$ \\
			\hline
		\end{tabular}
	\end{minipage}
	\caption{Approximate values of $B_n$ for various values of $n$}
	\label{table:walsh_bounds}
\end{table}

>>>>

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		$a$ & $(0,0)$ & $(0,1)$ & $(1,1)$ \\ \hline
		$\Dnka{2}{0}{a}$ &$1$&$1$ & $1$\\ \hline
		$\Dnka{2}{1}{a}$ &$2$& $0$ & $-2$\\ \hline
		$\Dnka{2}{2}{a}$ &$-1$&$1$ & $-1$\\ \hline
	\end{tabular}
	\tablecaption{Values of $\Dnka{2}{k}{a}$}\label{tab:Dnka}
\end{table}

@@

Denoting by $b$ the vector $\pi(a)+(0,1,0,1,\ldots,0,1)$, we can write the Walsh transform of $f$ in $a$ as:
\[ \wt{f}(a)=1+\sum_{k=1}^n\Dnka{n}{k}{b+\pi(e_k)}.\qedhere\]
\end{proof}

@@

    \begin{table}
    	\centering
    	\begin{tabular}{|c|c|}
    		\hline
    		$k$ & $\Dnka nka$\\ \hline
    		$0$&$1$\\ \hline
            $1$&$2(p-q)$\\ \hline
            $2$&$2(p-q)^2-3(p+q)+r$\\ \hline
            $3$&$\frac 23(p-q)\left(2(p-q)^2-9(p+q)+3r+7\right)$\\ \hline
    	\end{tabular}
    	\tablecaption{Values of $\Dnka{n}{k}{a}$ for small values of $k$}\label{tab:Dnka_small_k}
    \end{table}
\end{remark}

@@

	We prove that the maximum of $\left|-z^2+2z+1\right|$ on $\dis$ is $2\sqrt 2$ by showing that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$.
    %It remains to prove that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ equals $8$. 
    Using that $|w|^2=w\overline w$ for every complex number $w$, we obtain for all $z\in \dis$:
    \[
        \left|-z^2+2z+1\right|^2=\left(z^2-2z-1\right)\left(\overline z^2-2\overline z-1\right)=6-\left(z^2+\overline z^2\right)=6-2\mathrm{Re}\left(z^2\right),
    \]
    where $\mathrm{Re}\left(z^2\right)$ denotes the real part of $z^2$. Since the minimum of $\mathrm{Re}\left(z^2\right)$ on $\dis$ is $-1$, we conclude that the maximum of $\left|-z^2+2z+1\right|^2$ on $\dis$ is $6-2(-1)=8$.
\end{proof}

@@

	\begin{align*}
\wtk{d_{t,n}}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,n}(x)+a \cdot x}=\sum_{x \in \Ekn{k}{n}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}=\sum_{\ell=0}^{2t} \sum_{\substack{y \in \Ekn{\ell}{2t}\\z \in \Ekn{k-\ell}{n-2t}}} (-1)^{d_{t,2t}(y)+b \cdot y +c \cdot z}\\
&=\sum_{\ell=0}^{2t} \sum_{y \in \Ekn{\ell}{2t}} (-1)^{d_{t,2t}(y)+b \cdot y} \left( \sum_{z \in \Ekn{k-\ell}{n-2t}} (-1)^{c \cdot z}\right)=\sum_{\ell=0}^{2t} \Dnka{2t}{\ell}{b} \kraw{k-\ell}{\w(c)}{n-2t}.\qedhere
\end{align*}

@@

    \begin{figure}
    	\centering
    	\includegraphics[width=11cm]{family_curves_g.pdf}
    	\caption{The curves of $\alpha\mapsto g_\lambda(\alpha)$ for the values $\lambda=\frac{i}{25}$ from $i=0$ (blue) to $i=24$ (red).}
    	\label{fig:family_curves_g}
    \end{figure}

@@

\iffalse
\begin{table}
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
		$2$  & $2$     & $4$     \\
		$4$  & $8$     & $14$     \\
		$6$  & $20$    & $36$    \\
		$8$  & $52$    & $114$    \\
		$10$ & $108$   & $288$   \\
		$12$ & $292$   & $820$   \\
		$14$ & $700$   & $2\,316$  \\
		$16$ & $2\,176$  & $6\,006$  \\
		$18$ & $4\,964$  & $18\,192$  \\
		$20$ & $14\,968$ & $48\,480$ \\
		$22$ & $34\,232$ & $140\,392$ \\
		$24$ & $109\,648$ & $392\,168$ \\ \hline
	\end{tabular}
	\tablecaption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$}
	\label{table:max_walsh_vs_bound}
\end{table}
\fi

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$  & $\lfloor 1+n \cdot 2^{3n/4} \rfloor$\\ \hline
		$2$  & $2$     & $4$  &  $6$ \\
		$4$  & $8$     & $14$  & $33$  \\
		$6$  & $20$    & $36$   & $136$\\
		$8$  & $52$    & $114$  & $513$ \\
		$10$ & $108$   & $288$  & $1\,811$\\
		$12$ & $292$   & $820$  & $6\,145$ \\
		$14$ & $700$   & $2\,316$ & $20\,275$ \\
		$16$ & $2\,176$  & $6\,006$ & $65\,637$ \\
		$18$ & $4\,964$  & $18\,192$ & $208\,535$ \\
		$20$ & $14\,968$ & $48\,480$ & $655\,361$ \\
		$22$ & $34\,232$ & $140\,392$ & $2\,039 \,002$ \\
		$24$ & $109\,648$ & $392\,168$ & $6\,291 \,457$  \\ \hline
	\end{tabular}
	\tablecaption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$ and the one from Corollary~\ref{cor:bound_walsh_cauchy}.}
	\label{table:max_walsh_vs_bound}
\end{table}

\begin{table}
	\centering
	\begin{minipage}{0.24\textwidth}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			$n$ & $\approx B_n$ \\
			\hline
			$2$  & $4.00 \cdot 10^{0}$  \\
			$4$  & $1.40 \cdot 10^{1}$  \\
			$6$  & $3.60 \cdot 10^{1}$  \\
			$8$  & $1.14 \cdot 10^{2}$  \\
			$10$ & $2.88 \cdot 10^{2}$  \\
			$12$ & $8.20 \cdot 10^{2}$  \\
			$14$ & $2.32 \cdot 10^{3}$  \\
			$16$ & $6.01 \cdot 10^{3}$  \\
			$18$ & $1.82 \cdot 10^{4}$  \\
			$20$ & $4.85 \cdot 10^{4}$  \\
			\hline
		\end{tabular}
	\end{minipage}%
	\begin{minipage}{0.24\textwidth}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			$n$ & $\approx B_n$ \\
			\hline
			$22$ & $1.40 \cdot 10^{5}$  \\
			$24$ & $3.92 \cdot 10^{5}$  \\
			$26$ & $1.14 \cdot 10^{6}$  \\
			$28$ & $3.12 \cdot 10^{6}$  \\
			$30$ & $8.90 \cdot 10^{6}$  \\
			$32$ & $2.50 \cdot 10^{7}$  \\
			$34$ & $7.14 \cdot 10^{7}$  \\
			$36$ & $2.04 \cdot 10^{8}$  \\
			$38$ & $5.75 \cdot 10^{8}$  \\
			$40$ & $1.62 \cdot 10^{9}$  \\
			\hline
		\end{tabular}
	\end{minipage}%
	\begin{minipage}{0.24\textwidth}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			$n$ & $\approx B_n$ \\
			\hline
			$42$ & $4.59 \cdot 10^{9}$  \\
			$44$ & $1.29 \cdot 10^{10}$ \\
			$46$ & $3.63 \cdot 10^{10}$ \\
			$48$ & $1.02 \cdot 10^{11}$ \\
			$50$ & $2.88 \cdot 10^{11}$ \\
			$52$ & $8.06 \cdot 10^{11}$ \\
			$54$ & $2.30 \cdot 10^{12}$ \\
			$56$ & $6.45 \cdot 10^{12}$ \\
			$58$ & $1.83 \cdot 10^{13}$ \\
			$60$ & $5.14 \cdot 10^{13}$ \\
			\hline
		\end{tabular}
	\end{minipage}%
	\begin{minipage}{0.24\textwidth}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			$n$ & $\approx B_n$ \\
			\hline
			$62$ & $1.47 \cdot 10^{14}$ \\
			$64$ & $4.09 \cdot 10^{14}$ \\
			$66$ & $1.17 \cdot 10^{15}$ \\
			$68$ & $3.25 \cdot 10^{15}$ \\
			$70$ & $9.34 \cdot 10^{15}$ \\
			$72$ & $2.60 \cdot 10^{16}$ \\
			$74$ & $7.44 \cdot 10^{16}$ \\
			$76$ & $2.08 \cdot 10^{17}$ \\
			$78$ & $5.97 \cdot 10^{17}$ \\
			$80$ & $1.65 \cdot 10^{18}$ \\
			\hline
		\end{tabular}
	\end{minipage}
	\tablecaption{Approximate values of $B_n$ for various values of $n$}
	\label{table:walsh_bounds}
\end{table}
